Unveiling Robustness Threats by Mining the Exception Stack Traces of over 600 Android Projects

### 2014-09-05 android-stacks.tex
related

\textit{Detecting Faults on Java Exception-Related Code.}  Some tools have been 
proposed to detect faults  
on the exception handling code either statically (cabral, roberta,nelio,chang) 
or dynamicaly through testing (roberta). Both approaches, however, have inherent
 limitations. On the one hand, the static analysis tools needs to deal with the false 
positives and cannot adequately deal with dynamically loaded code (e.g. reflection  
[ref]). On the other hand the testing tools are llimited to the fact that the developer
 needs to create a test to exercise every exception, which is also costly.... (olhar tese). 
Moreover, both methods fail to account for exceptions implicitly signaled by the runtime 
environment (e.g. due to resource depletion which can be signaled in every statement invocation).

Robillard and Murphy~\cite{Robil00} employed dataflow analysis to find the propagation paths of checked and
unchecked exception types. Modeled after Robillard and Murphy's work, other
tools have been proposed to support the static analysis of exception
flows~\cite{coelho2008assessing}. The main limitation of all
static analysis tools is the number of false positives inherent to static analysis
solutions, which can lead to a high number of exception flows, specially if
considering Java Environment exceptions and exceptions signaled from libraries.

Additionally, Cabral and Marques~\cite{cabral2007exception} analyzed the
exception handling code of 32 open-source systems, both for Java and .NET. They
observed that the action handlers were very simple (e.g., logging and present a
message to the user). Reimer and Srinivasan~\cite{reimer2003analyzing} listed a
set of bad practices on exception handling that hinder software maintainability
and robustness, based on their own experience with Java enterprise applications.
Our work differs from those two works as we tried to identify bad practices from
the analysis of stack traces extracted from issues in combination with and bytecode and source
code analysis. \footnote{ to do: TODORESSALTAR LIMITACAO DE QUANTIDADE DE FALSOS POSITIVOS... E QUE OS STACKS SAO REAIS...
REPRESENTAM FLUXOS REAIS.... POST MOSTERN ANALISYS OF REAL EXECUTIONS....}

>>>>

\textit{Detecting Faults on Java Exception-Related Code.} 
Cabral and Marques~\cite{cabral2007exception} analyzed the
source-code of 32 open-source systems, both for Java and .NET. They
observed that the action handlers were very simple (e.g., logging and present a
message to the user). Reimer and Srinivasan~\cite{reimer2003analyzing} listed a
set of bad practices on exception handling that hinder software maintainability
and robustness, based on their own experience with Java enterprise applications.
Our work differs from those

Some tools ~\cite{Robil00}~\cite{coelho2008assessing} have ben proposed 
to employ dataflow analysis to find the propagation paths of checked and unchecked 
exception types. The main limitation of all static analysis tools is the number of false 
positives inherent to static analysis solutions, which can lead to extremely high number 
of exception flows, specially if considering Java Environment exceptions and exceptions 
signaled from libraries. Moreover, such also have limited support some libraries (e.g., Java Reflection).
Our owrk
